### 2016-09-23 results.tex
counterexample for SS-privacy of bigram linear

\begin{theorem}\label{thm:lin-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B} + \mbox{[TBD]}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}[Proof (sketch). ]
\end{proof}

>>>>

\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Should follow from Jon's general result(?)}

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
\heading{Bigram Linear-PRF construction (``Neidermayer''). }
\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}

%Next we consider the privacy of this construction, relative to a leakage function that behaves as follows.  On input a set $S=\{x_1,x_2,\ldots,x_n\}$, it computes $B_i \gets \mathsf{bigram}(x_i)$ for each $i \in [n]$.  Then, for all $1 \leq c \leq p$, and all size-$c$ subsets $\{j_1,j_2,\ldots,j_c\} \subseteq p$, it computes $L{j_1,j_2,\ldots,j_c}=|B_{j_1} \cap B_{j_2} \cap \ldots \cap B_{j_c}|$.  That is, it computes all of the $c$-way intersections. It returns $|S|=n$ and all of the $2^p -1$ intersection sizes as the leakage. \todo{Explain why this is plausibly leaked by $\pubaux$ for this construction.} \tsnote{This is exponential in size, so that means a simulator that reads the entire leakage will also be exponential-time in~$p$.  } \tsnote{Should we be considering smaller, but less realistic leakage, like $\mathsf{leak}(S)=S\setminus\{x\}$.}

Next we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.  Consider the following leakage function.  On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak}(S)=\{x_1,x_2,\ldots,x'_n\}$.

\begin{figure}
\centering
\fpage{.5}
{
\adversaryv{A}\\
On input $\emptystring$:\\
\nudge $x_1 \gets \mathrm{cab}$\\
\nudge $x_2 \gets \mathrm{bab}$\\
\nudge $z \getsr \bits$\\
\nudge if $z=1$ then $x_3 \gets \mathrm{caba}$\\
\nudge else $x_3 \gets \mathrm{cabc}$\\
\nudge Return $S=\{x_1,x_2,x_3\}$\\
On input $\pub \neq \emptystring$:\\
\nudge $M_1,M_2,M_3 \gets \pub$\\
\nudge $M_{1,2} \gets M_1 \vee M_2$\\
\nudge if $z=1 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) = 4k\right)$ then \\
\nudge\nudge Return 1 \\
\nudge if $z=0 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) = 3k\right)$ then \\
\nudge\nudge Return 1 \\
\nudge Return 0
}
\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}}
\label{fig:adv-bi-lin-ss}
\end{figure}

\begin{theorem}\label{thm:bi-lin-ss}
Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K_1},F_{K_2}$ replaced by independent random functions~$\rho_1,\rho_2$ (respectively).  Let $\leak$ be the leakage function just described.   Let~$\univ=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$,
the advantage $\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.

\end{theorem}
\begin{proof}(Sketch.)
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability (up to collisions in the hash functions for different bigrams within a given bigram set).   Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.

In the case that $B_{x_3}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, only one of its elements ($\mathrm{a}\sqcup$) is not in either of $B_{x_1},B_{x_2}$.  Hence, the hamming weight of $M_{1,2}\wedge M_3$ will be $4k$.  On the other hand, when $B_{x_3} = \{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, two of its elements ($\mathrm{bc}, \mathrm{c}\sqcup$) are not covered by $B_{x_1},B_{x_2}$.  In this case, the hamming weight of $M_{1,2} \wedge M_3$ will be $3k$.  Thus $\ExpPrivSSreal{\Pi_{\mathrm{bi-lin}}}{A}=1$ with overwhelming probability.

On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random functions~$\rho_1,\rho_2$ itself.  However, it has no information about the bit~$z$, so at best it can cause~$A$ to output 1 with probabilility~$1/2$.
\end{proof}
